### 2017-09-01 monograph/thesis/chapters/chapter_1.tex
Updated the pretexto remaining templates with ufscthesisx.
Added machine translation to chapter_1.tex until the translation is
finished.

\cleardoublepage
\phantomsection

% The \phantomsection command is needed to create a link to a place in the document that is not a
% figure, equation, table, section, subsection, chapter, etc.
\addcontentsline{toc}{chapter}{\texorpdfstring{\MakeTextUppercase{Capítulo 1}}{Capítulo 1}}

\chapter{Capítulo 1}

\newpage

\section{Introdução}

    Perguntas como ``O que são boas práticas de programação?'' ou ainda ``O por quê estas práticas
    são boas?'', não são fáceis de responder. Mas cada programador aprende a escrever seus códigos
    em uma determinada maneira, com determinadas características como utilizar 4 ou 8 espaços para
    indentação de linhas, sempre deixar uma linha em branco antes de cada estrutura de controle como
    if\textquotesingle s, for\textquotesingle s, e afins.

@@

    Assim no final da primeira parte desta obra que dará-se no final da conclusão da disciplina
    intitulada de Trabalho de Conclusão de Curso 1, restarão somente as informações destinadas a
    implementação da ferramenta proposta, que serão implementadas na segunda parte da monografia
    denominada \nameref{sec:implementation}, que será desenvolvida no final da conclusão da
    disciplina de Trabalho de Conclusão de Curso 2.

>>>>

% The \phantomsection command is needed to create a link to a place in the document that is not a
% figure, equation, table, section, subsection, chapter, etc.
%
% When do I need to invoke \phantomsection?
% https://tex.stackexchange.com/questions/44088/when-do-i-need-to-invoke-phantomsection
\cleardoublepage
\phantomsection

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{\chooselang{Introduction}{Introdução}}

\chooselang
{
    Questions like ``What are good programming practices?'' Or ``Why these practices
    are they good?'', are not easy to answer. But every programmer learns to write their codes
    in a certain way, with certain features like using 4 or 8 spaces to
    indentation of lines, always leave a blank line before each control structure as
    if for example, for \textquotesingle, and the like.

    But entering the universe of good practices, there are many things about discoursing. Thus in this work
    specifically work out how to perform the best layout / display of
    computer screen, so that it maximizes and facilitates its understanding.
    Therefore allowing the programmer to disperse more tempe thinking about the problem, than
    try to decipher the information that is presented to him on the screen.

    Within this area of work, you also need to think very carefully about how to share the
    programming codes among programmers. This is why the problem of
    diversity of good programming practice. It happens because often, what is a
    good practice for one `programmer A ', it is not for the other` programmer B'. For example, imagine a
    code where a programmer decided to put before each `if ', a blank line. So it is
    expected that whenever we see a blank line we can potentially find
    `if '. However imagine that another programmer did not like this rule and when he went to write
    his code that involved an `if ', he did not put such a blank line as the other
    programmer had been putting. So when the first programmer reads the code and looks for
    `if'es, it will be waiting for blank lines. But you're going to spend some time looking
    realize that the other programmer has not put them on.

    These differences are due to the diversity of means of learning programming, as much as
    to the tastes, aptitudes and goals of each programmer. So today it becomes a great
    problem as we increasingly need more and more programmers working together between
    themselves, developing the most diverse computational systems. Where the latter is due to the fact that
    complexity of computing systems is increasing, so it is
    more programmers work and share codes.

    So besides just worrying about how the code is displayed on the computer screen, we
    we need to worry about how it will be saved in the file system. Since the
    code, it is vital to use a versioning system to allow
    projects and programmers themselves, have control of code changes. What I allowed and
    can easily track change and enable you to better understand
    that each programmer is doing each time he formalizes a change in the code through
    a `commit ', as in` git` systems, for example.

    This is why when working on a versioning system like `git 'we need to keep the
    code between a single style or good practice defined as standard, due to the fact that
    letting each programmer write as he wants, we will have a lot of noise during the review of
    code and we are determining what the programmer did / wrote, if each programmer re-writes the
    making historical changes like putting new lines before each if. So we will have noise for
    that the focus of a versioning system is to look only at changes that are significant
    to the code, such as creating new functions and not adding new blank lines.

    On the last point, we can also think about an approach to the creation of a new
    version that only focuses on the significant changes to the code, during the moment of the
    review. However, this approach is not ideal because, for example, it gives
    programmers engage in daunting and unproductive wars of code adjustments. For example,
    imagine how it would be every day that you wake up and start working, you have to go through
    code by placing new lines before each of the if \textquotesingle s because the programmer's
    night shift had just removed them?

\section{Goals}

    Establish relationships between good programming practices and efficiency in programming, as well as
    new tool to support the programmer in order to automate the long and diverse process
    of programming in teams of developers with different good programming practices.

\subsection{Specific objectives}

        A study on universal programming tools, allowing
        software, be programmed in all programming languages. So explain the
        differences for other software and why you want a unique tool, instead
        of several.

        Define, study, determine and classify what are good programming practices and perform
        an in-depth study on good practice in the area of visual
        also like `Beautifying '.

        A study on the most diverse tools available to support good
        programming, as well as a comparative analysis between them, determining their weaknesses and
        Strong points.

        The definition of a development flox pattern that allows teams of programmers
        with different good programming practices, work on themselves without intervening and start wars
        good practice.

        To propose a unique tool that allows several different good programming practices to be
        implemented in the most diverse programming languages and that they can be configured
        and defined to the liking of the programmers who use it.

\section{Search method}

    The work will be based on research in articles, books, theses, dissertations, authors' websites
    reliable, and through new evidence demonstrated and based on arguments in the course of
    of the evolution of the monograph. It will also present the results of the construction of a
    new tool that proposes the solution of one of the problems presented and explained.

    The last chapter of this proposal is in the topic \autoref{sec:implementation}
    a series of links and references that are pre-selected and can be used in the
    final construction of this work. Notes that in themselves, the parts of the last section will be gradually
    moved to the first part of the text where theoretical research is found, in the course of which its
    information is incorporated into the written work.

    So at the end of the first part of this work that will take place at the conclusion of the discipline
    Course Completion Work 1, there will be only information
    implementation of the proposed tool, which will be implemented in the second part of the monograph
    called \nameref{sec:implementation}, which will be developed at the end of the
    discipline of Course Completion Work 2.
}

{
    Perguntas como ``O que são boas práticas de programação?'' ou ainda ``O por quê estas práticas
    são boas?'', não são fáceis de responder. Mas cada programador aprende a escrever seus códigos
    em uma determinada maneira, com determinadas características como utilizar 4 ou 8 espaços para
    indentação de linhas, sempre deixar uma linha em branco antes de cada estrutura de controle como
    if\textquotesingle s, for\textquotesingle s, e afins.

@@

    Assim no final da primeira parte desta obra que dará-se no final da conclusão da disciplina
    intitulada de Trabalho de Conclusão de Curso 1, restarão somente as informações destinadas a
    implementação da ferramenta proposta, que serão implementadas na segunda parte da monografia
    denominada \nameref{sec:implementation}, que será desenvolvida no final da conclusão da
    disciplina de Trabalho de Conclusão de Curso 2.
}
